---
title: "CSVFileImport"
output: html_notebook
---

# Load Libraries
```{r,  warning=FALSE,include= TRUE,echo=TRUE,results='hide', message=FALSE}
#install.packages("dplyr")
#install.packages("stringr")
#install.packages(graphics)
#install.packages("ggplot2")

# load installed libraries 
library(tools)
library(plyr)
library(dplyr)
library(stringr)
library(graphics)
library(ggplot2)
library(yaml)
```

# Load DB Meta Data 
```{r}
db_urls = read.csv('../data/database_list.csv', header=TRUE, encoding = "UTF-8", na.strings = "null")
db_infos = read.csv('../DBEngines/DBRanking.csv', header=TRUE, encoding = "UTF-8", na.strings = "null") 

```

# Create Base-Dataframe
```{r}
# get the names of the preselected DBs
names = as.vector(db_urls$URLName)  

# select preselected entries 
selected_rows = db_infos[tolower(db_infos$URLName) %in% tolower(names), ]

# remove "Rank"-column
tmp_df = db_urls[,!(names(db_urls) %in% c("Rank"))]

# create a dataframe with information about the preselected DBs
base_df =  right_join(selected_rows, tmp_df, by = "URLName")

# remove following unused data
rm(names, selected_rows, tmp_df, db_urls, db_infos)

```

# Cleaning and Prepping Data
```{r}
# Remove unneccesary columns
drop_list = c("Name", "Ausschließlich.ein.Cloud.Service", "DBaaS.Angebote", "Anmerkung")
result_meta_df = base_df[ , !(names(base_df) %in% drop_list)]

# remove following unused data
rm(base_df)

# check the values class
# lapply(result_meta_df$Rang, class)

# The following variables were imported as factors, but they should be numerical 
columns_to_numeric = c("Punkte", "Rang", "Suchmaschinen","Erscheinungsjahr", 
                       "Graph.DBMS", "Document.Stores", "Key.Value.Stores", "Relational.DBMS",
                       "Time.Series.DBMS", "Multivalue.DBMS", "Object.oriented.DBMS", "RDF.Stores", 
                       "Wide.Column.Stores", "Navigational.DBMS", "Event.Stores", "Native.XML.DBMS",
                       "Content.Stores")
result_meta_df[columns_to_numeric] = lapply(result_meta_df[columns_to_numeric], as.numeric)

# The following variables were imported as factors, but they should be characters
columns_to_chr = c("Kurzbeschreibung", "Website", "Technische.Dokumentation", "Entwickler",
                    "Aktuelle.Version", "Server.Betriebssysteme", "Git_URL")
result_meta_df[columns_to_chr] = lapply(result_meta_df[columns_to_chr], as.character)

# remove following unused data
rm(drop_list, columns_to_numeric, columns_to_chr)

```

```{r}
cor(result_meta_df[ , c( "Punkte", "Rang")], use="complete")
```

```{r}
db_df = data.frame(
  names1 = c("MySql","PostgreSQL", "MongoDB", "ElasticSearch", "Redis"),
  ranking = c(2, 4, 5, 7, 8),
  commits = c(152906, 48124, 49221, 49375, 8631),
  contributers= c(72, 33, 393, 1310, 319)
)

cor(db_df[ , c("ranking", "commits", "contributers")], use="complete")
# the negative correlation of ranking-commits is justified by the inversely proportional value of the rank to the rank itself
# the lesser the rank, the higher it's value 

# log(R)

```

```{r}
color = c("red", "blue", "green", "orange", "black")

plot(db_df$ranking~db_df$commits, type = "p", pch =19, main = "Ranking in dependence of Commits", col= color, ylim = rev(range(db_df$ranking)), xlab="Commits", ylab="Rank")

legend("bottomright", legend = db_df$names1, col = color, pch=19, cex=0.8)

```

```{r}
plot(db_df$commits~db_df$contributers, type = "p", pch =19, main = "Commits in dependence of Contributers", col= color, xlab="Contributers", ylab="Commits")

legend("topright", legend = db_df$names1, col = color, pch=19, cex=0.8)

```

```{r}
plot(db_df$ranking~db_df$contributers, type = "p", pch =19, main = "Ranking in dependence of Contributers", col= color, ylim = rev(range(db_df$ranking)), xlab="Contributers", ylab="Rank")

legend("topright", legend = db_df$names1, col = color, pch=19, cex=0.8)

```









# Load Git-History for DB
# (default-branch)
```{r}

# Git-History for DBs (default-branch)
db_git_history = read.csv('../Workspace/PostgreSQL.csv', header=TRUE, encoding = "UTF-8", na.strings = "null", sep = ";")

file_extensions = yaml.load_file('../data/file_extension/languages.yml')

```

```{r}
# Convert timestamp from factor to POSIXct format
db_git_history["timestamp"] = lapply(db_git_history["timestamp"], function(x) as.POSIXct(x, format='%Y-%m-%dT%H:%M:%S'))

ext_key = list()
ext_value = list()

tmp_names = names(file_extensions)

i=1

for(name in tmp_names){
  tmp_list = file_extensions[name]

  # removes all File Extensions but Programming Languages
  if(tmp_list[[name]]$type != "programming"){
    next;
  }
  
  for(extension in tmp_list[[name]]$extensions){
    ext_key[i] = extension
    ext_value[i] = name
    i = i + 1
  }
}
rm(tmp_list, extension, i, name)
rm(file_extensions)

ext_map = data.frame(extension = unlist(ext_key, use.names=FALSE), programmingLanguage = unlist(ext_value, use.names = FALSE))
rm(ext_key, ext_value)


test = function(x){
  ext = paste(".", as.character(tail(unlist(str_split(x, "[.]")), 1)), sep="")

  ifelse(ext %in% ext_map$extension,
          as.character(ext_map$programmingLanguage[match(ext, ext_map$extension)]),
         "unknown")
}

test2 = function(x){
  lapply(x, test)
}

db_git_history["programmingLanguage"] = lapply(db_git_history["file"], function(x) test2(x))



# Flatten the resulting List to a vector
db_git_history["programmingLanguage"] = unlist(db_git_history$programmingLanguage, use.names=FALSE)

# Convert the FileExtensions to factors
db_git_history$programmingLanguage = as.factor(db_git_history$programmingLanguage)

# provisionally renamed: "result" marks the data frames to plot with
result_git_df = db_git_history

```

# Plots


# Fragenstellung:
# Wie Teilen Sich die Entwickler den Code auf? Hat jeder seinen Bereich? Wieviel Overlap ist vorhanden?

## pie chart programmiersprachen in projekt
```{r}
plot_pie_chart = function(threshold, db_git_history){

  tmp = aggregate(db_git_history$change, by = list(programmingLanguage = db_git_history$programmingLanguage), FUN = sum)
  tmp = tmp[!(tmp$programmingLanguage == "unknown"),]
  tmp_sum = sum(tmp$x)

  tmp = mutate(tmp, x = x / tmp_sum * 100)

  add_df = data.frame("others" , sum(tmp[tmp$x <= threshold,]$x))
  names(add_df) = c("programmingLanguage", "x")

  tmp = tmp[tmp$x > threshold,]

  tmp = rbind(tmp, add_df)


  bp<- ggplot(tmp, aes(x="", y=x, fill=programmingLanguage))+
  geom_bar(width = 1, stat = "identity")

  pie <- bp + coord_polar("y", start=0)
  
  return(pie + scale_fill_brewer(palette="Dark2"))
}

plot_pie_chart(1, db_git_history)


```

## top 5-10 pro entwickler anteil sprachen

```{r}



```


## top 5-10 pro programmiersprache anteil entwickler
## histogramm, xachse= programmiersprache, yachse=anzahl(Verwendung, commit)
## histogram anteil programmiersprache pro commit

